Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

>>>>

# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
